%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Eunhee Kim} \\ \vspace{1pt}
    \href{mailto:eunhee.dev@gmail.com}{\underline{eunhee.dev@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/eun-hee-kim/}{\underline{linkedin.com/in/eun-hee-kim}} $|$
    \href{https://github.com/eunhee-dev}{\underline{github.com/eunhee-dev}}
\end{center}

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

% \section{Experience}
%     \resumeSubheading
%       {AI Research Engineer}{Aug 2024 -- Present}
%       {Cinamon Inc.}{Seoul, South Korea}
%       \resumeItemListStart
%         \resumeItem{Communicate with managers to set up campus computers used on campus}
%         \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
%         \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
%     \resumeItemListEnd

%     \resumeSubheading
%       {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
%       {Southwestern University}{Georgetown, TX}
%       \resumeItemListStart
%         \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
%         \resumeItem{Developed a game in Java to test the generated dungeons}
%         \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
%         \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
%         \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
%         \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
%       \resumeItemListEnd
%   % \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {AI Research Engineer}{Aug 2024 -- Present}
    {Cinamon Inc.}{Seoul, South Korea}
    \resumeItemListStart
      \resumeItem{Developed generative motion models for \href{https://cinev.com/en}{CineV}, video generation service based on LLMs and Unreal Engine}
      \resumeItem{Implemented generative models for text-to-motion, motion refinement, stylization, in-betweening, and part-aware composition}
      \resumeItem{Optimized and served ML models using Triton, ONNX, TorchServe, achieving 10x faster inference}
      \resumeItem{Managed orchestration of automated data preprocessing pipelines using Airflow and Dagster}
    \resumeItemListEnd

  \resumeSubheading
    {Intern Researcher}{Sep. 2021 -- Feb 2022}
    {Gwangju Institute of Science and Technology}{Gwangju, South Korea}
    \resumeItemListStart
      \resumeItem{Conducted data analysis on factors affecting user churn in online games}
    \resumeItemListEnd

  \resumeSubheading
  {Teaching Assistant}{Nov. 2020 -- Nov. 2020}
  {Korea Social Science Data Archive (KOSSDA)}{Remote}
  \resumeItemListStart
  \resumeItem{Teaching Assistant for the KOSSDA Research Methodology Workshop, Introduction to Statistical Analysis with R}
  \resumeItem{Assisted with hands-on sessions covering statistical analysis}
  \resumeItemListEnd

  \resumeSubheading
  {Research Staff (Team Leader)}{Feb. 2018 -- Nov. 2018}
  {Survey Research Center, Sungkyunkwan University}{Seoul, South Korea}
  \resumeItemListStart
  \resumeItem{Conducted face-to-face social survey interviews in the Seoul and Gyeonggi regions}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gwangju Institute of Science and Technology (GIST)}{Gwangju, South Korea}
      {Master of Science in Integrated Technology (Graduate Program of Culture Technology)}{Mar. 2022 -- Feb. 2024}
        \resumeItemListStart
          \resumeItem{Supervisor: Kyung-Joong Kim}
          \resumeItem{\href{https://cilab.gist.ac.kr/hp/}{Cognition and Intelligence Lab}}
          \resumeItem{Cumulative GPA: 4.25/4.5}
        \resumeItemListEnd
    \resumeSubheading
      {Kyung-Hee University}{Seoul, South Korea}
      {Bachelor of Arts in Sociology and Bachelor of Science in Applied Mathematics}{Mar. 2017 -- Aug. 2021}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 4.04/4.5}
      \resumeItemListEnd
    \resumeSubheading
      {University of Turku}{Turku, Finland}
      {Exchange Student Program, Mathematics}{Aug. 2019 -- Dec. 2019}
  \resumeSubHeadingListEnd

      


%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Controllable Long-term Motion Generation with Extended Joint Targets} 
          \\$|$ \emph{WACV}}{Mar. 2026}
          \resumeItemListStart
            \resumeItem{Eunjong Lee, \textbf{Eunhee Kim}, Sanghoon Hong, Eunho Jung, Jihoon Kim}
            \resumeItem{\href{https://comet-proj.github.io}{Project Page} $|$ \href{https://openaccess.thecvf.com/content/WACV2026/html/Lee_Controllable_Long-term_Motion_Generation_with_Extended_Joint_Targets_WACV_2026_paper.html}{Paper} $|$ \href{https://youtu.be/vZh8PwArOe0?si=MOItkrb3HT2LwRAU}{Video}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{DAncing body, Speaking Hands (DASH): Sign Dance Generation System with Deep Learning} 
          \\ $|$ \emph{SIGGRAPH Poster}}{Jul. 2023}
          \resumeItemListStart
            \resumeItem{\textbf{Eunhee Kim}, Taehwa Park, Jaeyoung Moon, Wonsang You, Taegwan Ha, Kyung-Joong Kim}
            \resumeItem{\href{https://dl.acm.org/doi/abs/10.1145/3588028.3603687}{Paper}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    

%
%-----------PATENTS-----------
\section{Patents}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://doi.org/10.8080/1020230061217}{10-2023-0061217}}{, Motion Feedback Method and System using Normalized Data} \\
    }}
 \end{itemize}

% %-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Visualize Music and Dance for the Hard-of-Hearing to Enjoy Music} $|$ \emph{KOCCA}}{Mar. 2022 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Developed music-to-motion generation model based on VQ-VAE and Diffusion Models}
            \resumeItem{Implemented `Sign Dance' generating system, incorporating sign language to dance}
            \resumeItem{In-the-wild data preprocessing from video to SMPL motion data using human pose estimation}
            \resumeItem{Built Korean sign language motion-text paired database of 35,000 frames}
            \resumeItem{\href{https://n.news.naver.com/mnews/article/056/0011492822?sid=103}{Press}}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{HCI + AI for Human-Centered Physical System Design} $|$ \emph{GIST, MIT CSAIL}}{Mar. 2022 -- May. 2024}
          \resumeItemListStart
            \resumeItem{Developed real-time physical systems for estimating human pose from multi-view video and pressure-sensing data}
            \resumeItem{Implemented virtual assistant with Transformer-based muscle EMG prediction model from pressure-sensing data}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Groovy Graph} $|$ \emph{Pseudo Lab (Non-profit AI Research Organization)}}{Mar. 2022 -- Jul. 2022}
          \resumeItemListStart
            \resumeItem{Weekly academic paper review of graph neural networks}
            \resumeItem{\href{https://chanrankim.notion.site/Groovy-Graph-1a98bd335501499e894efd5a79efe479}{Project Page} $|$ \href{https://pseudo-lab.github.io/graph/}{Team Blog}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical Skills}{: Python, PyTorch, Triton, ONNX, TorchServe, FastAPI, W\&B, TensorBoard} \\
     \textbf{Graphics Tools}{: Blender, Photoshop, Illustrator} \\
     \textbf{Developer Tools}{: Git} \\
     \textbf{Languages}{: Korean (Native), English (Fluent)}
    }}
 \end{itemize}



%-----------SELECTED HONORS-----------
\section{Selected Honors}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Best Game AI Jam Project}{Chania, Greece}
      {International Summer School on AI and Games}{2022}
    \resumeSubheading{Scholarship for Activities of International Affairs}{Seoul, South Korea}{Kyung-Hee University}{2020}
    \resumeSubheading{Dream Scholarship of Research}{Seoul, South Korea}{Kyung-Hee University}{2019 -- 2020}
    \resumeSubheading{Scholarship for Professor-Tutor-Student Portfolio}{Seoul, South Korea}{Kyung-Hee University}{2018 -- 2019}
    \resumeSubheading
    {Superior Scholarship}{Seoul, South Korea}{Kyung-Hee University}{2017}
    \resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\section{Certificates \& Test Scores}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Survey Analyst}{, Junior (Sep. 2020)} \\
     \textbf{OPIc}{, IH (Mar. 2026)} \\
     \textbf{TOEIC}{, 905 (Oct. 2023)} \\
     \textbf{TOEFL}{, 92 (Sep. 2018)} \\
    }}
 \end{itemize}

\end{document}
